NFC and burnout in teachers - A replication and extension study

### 2022-02-23 Manuscript/Manuscript.tex
tried double backslash for &nbsp; but doesnt work

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={NFC and burnout in teachers - A replication and extension study},
  pdfauthor={Josephine Zerna1, Nicole Engelmann2, Anja Strobel3, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={mediation, resources, demands, structural equation modelling, Covid-19},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

@@

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{NFC and burnout in teachers}
\keywords{mediation, resources, demands, structural equation modelling, Covid-19\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Josephine Zerna: Conceptualization, Methodology, Formal analysis, Writing - original draft preparation, Writing - review \& editing; Nicole Engelmann: Conceptualization, Investigation, Writing - review \& editing; Anja Strobel: Conceptualization, Supervision, Methodology, Writing - review \& editing; Alexander Strobel: Conceptualization, Supervision, Methodology, Writing - review \& editing.

Correspondence concerning this article should be addressed to Josephine Zerna, Zellescher Weg 17, 01069 Dresden, Germany. E-mail: \href{mailto:josephine.zerna@tu-dresden.de}{\nolinkurl{josephine.zerna@tu-dresden.de}}

}

@@

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

@@

@@

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities (Cacioppo \& Petty, 1982).
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm \& Ackerman, 2013), and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo \& Petty, 1982).
While many studies have found positive associations of NFC with academic performance (Cazan \& Indreica, 2014; Elias \& Loomis, 2002; Grass et al., 2017; Lavrijsen et al., 2021; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski \& Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020).
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe \& Kivimäki, 2013) to psychological (Madsen et al., 2017; Maslach \& Leiter, 2016; Wiesner et al., 2005).

One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly (Schaufeli \& Salanova, 2014).
Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer (Gray-Stanley \& Muramatsu, 2011; Lloyd et al., 2002).
Lackritz (2004) found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
Burnout is most often assessed using the Maslach Burnout Inventory (MBI) (Maslach et al., 1997), a self-report questionnaire with three subscales: Emotional exhaustion, depersonalisation, and reduced self-efficacy.

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control (Schaufeli \& Salanova, 2014).
NFC on the other hand is negatively associated with those variables (Double \& Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
This is supported by the findings that NFC is negatively associated with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Kantas \& Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021; \textbf{Brady?}) has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. (2018) investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively (Gross, 1998).
The findings by Grass et al. (2018) suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
One goal of this paper is to replicate the findings of Grass et al. (2018) using a multiple mediation model on cross-sectional self-report data of teachers.
We expect NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we would like to extend the analysis to other possible mediators.
These mediators are motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree (Zerna et al., 2021).
Only a balance of resources and demands results in personal wellbeing, while an imbalance threatens wellbeing, regardless of whether this imbalance is in favour of resources or demands (Dodge et al., 2012).
Following the framework of Hobfoll (1989), resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges (Cacioppo et al., 1996).
These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery (Salanova et al., 2006).
We would therefore like to investigate whether the association of NFC and burnout is mediated by different ratios of demands and resources; demands that are too high to be dealt with using one's personal resources (DTH), demands that are too low for one's personal resources (DTL), and a balanced fit of demands and resources (DRF).
Using the same data as for the replication, we compute a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities (Bye \& Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski \& Fauth, 1996), we expect NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
And since burnout results from constant unpleasant activation by high demands, we expect it to be positively associated with DTH and negatively associated with DRF.
However, we have no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli \& Salanova, 2014).

\emph{The Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe \& Franco, 2021).}

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript are available at \url{https://osf.io/36ep9/}.

@@

Teachers were recruited via social media, emails to colleagues of N.E. and to Saxon schools with the request to pass on the information.
All teachers were eligible, no payment was issued.
Of the \(N=\) 278 participants, who started filling out the online survey, \(N=\) 180 (72.20\% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
All of them were currently teaching at a primary, secondary, comprehensive, or vocational school.
Data was collected between the 12th of June and the 24th of July 2020.
At this point, schools had been switching between digital and hybrid forms of teaching for at least three months due to the Covid-19 pandemic, causing additional stress for many teachers.

@@

We used \emph{R Studio} (R Core Team, 2020; RStudio Team, 2020) with the main packages \emph{lavaan} (Rosseel, 2012) and \emph{psych} (Revelle, 2021) for all our analyses.

\hypertarget{multiple-mediation-model}{%
\subsubsection{\texorpdfstring{\emph{Multiple mediation model}}{Multiple mediation model}}\label{multiple-mediation-model}}

Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.

\hypertarget{structural-equation-model}{%
\subsubsection{\texorpdfstring{\emph{Structural equation model}}{Structural equation model}}\label{structural-equation-model}}

Items were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. (2019), a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.

\hypertarget{exploratory-analysis}{%
\subsubsection{\texorpdfstring{\emph{Exploratory analysis}}{Exploratory analysis}}\label{exploratory-analysis}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={NFC and burnout in teachers - A replication and extension study},
  pdfauthor={Josephine Zerna1, Nicole Engelmann2, Anja Strobel3, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={mediation, resources, demands, structural equation modelling, Covid-19},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{NFC and burnout in teachers}
\keywords{mediation, resources, demands, structural equation modelling, Covid-19\newline\indent Word count: ~ 5600}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage{chngcntr}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

@@

\abstract{
The prevalence of burnout has been rising for years, not just due to the increasing demands during the Covid-19 pandemic.
While it is known that burnout primarily affects employees in social jobs, less is known about the personality traits that promote or protect against burnout.
One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
In the present study, we analyzed questionnaire data of N = 180 teachers that had been collected in spring of 2020.
Firstly, we aimed to replicate results by Grass et al.~(2018), who showed that the association of NFC and the burnout aspect of reduced personal efficacy was mediated by habitual use of reappraisal, but not by habitual suppression or self-control.
With our data, self-control became a significant mediator when teaching experience was being taken into account, but neither reappraisal nor suppression mediated between NFC and reduced personal efficacy.
Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources, and included other variables in an exploratory approach.
The results indicated that teachers with higher NFC and more self-control have lower burnout because they experience their resources as fitting to their demands.
}

@@

\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\counterwithout{table}{section}
\setcounter{figure}{0}
\setcounter{table}{0}

@@

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities (Cacioppo \& Petty, 1982).
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm \& Ackerman, 2013), and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo \& Petty, 1982; German form: Bless et al., 1994).
While many studies have found medium sized positive associations of NFC with academic performance (Cazan \& Indreica, 2014; Grass et al., 2017; Lavrijsen et al., 2021; Stumm \& Ackerman, 2013; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski \& Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020), with these associations being small to medium sized by and large.
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe \& Kivimäki, 2013) to psychological consequences (Madsen et al., 2017; Maslach \& Leiter, 2016; Wiesner et al., 2005).

One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly (Schaufeli \& Salanova, 2014).
Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer (Gray-Stanley \& Muramatsu, 2011; Lloyd et al., 2002).
Lackritz (2004) found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
Burnout is most often assessed using the Maslach Burnout Inventory (MBI) (Maslach et al., 1997), a self-report questionnaire with three subscales: \emph{Emotional exhaustion}, a sense of fatigue and depletion, \emph{depersonalisation}, a negative attitude towards clients, along with a loss of idealism, and \emph{reduced personal efficacy}, a decline of capability and coping skills.

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control (Schaufeli \& Salanova, 2014).
NFC on the other hand is negatively associated with those variables (Double \& Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Brady et al., 2021; Kantas \& Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021) has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. (2018) investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively (Gross, 1998).
The findings by Grass et al. (2018) suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor (Strobel et al., 2017).
One goal of this paper was to replicate the findings of Grass et al. (2018) using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree (Zerna et al., 2021).
This can take the form of patients with higher NFC having lower intentions to consult their physician (Latimer et al., 2007) or adults with higher NFC having higher intentions to consume high calorie beverages (Gallivan, 2020) after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands (Dodge et al., 2012).
Following the framework of Hobfoll (1989), resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges (Cacioppo et al., 1996).
These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery (Salanova et al., 2006).
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one's personal resources (\emph{demands too high}), demands that are too low for one's personal resources (\emph{demands too low}), and a balanced fit of demands and resources (\emph{demand-resource-fit}).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities (Bye \& Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski \& Fauth, 1996), we expected NFC to be negatively associated with \emph{demands too high}, and positively associated with \emph{demands too low} and \emph{demand-resource-fit}.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with \emph{demands too high} and negatively associated with \emph{demand-resource-fit}.
However, we had no hypothesis regarding the association of \emph{demands too low} and burnout, because even though \emph{demands too low} is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli \& Salanova, 2014).
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe \& Franco, 2021), so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the R package \emph{papaja} (Aust \& Barth, 2020), are available at \url{https://osf.io/36ep9/}.
The procedure was evaluated and approved by the Ethics Committee of the Chemnitz University of Technology (reference number: V-389-15-AS-Burnout-08062020).
It was not considered to require further ethical approvals and hence, as uncritical concerning ethical aspects according to the criteria used by the Ethics Committee, which includes aspects of the sample of healthy adults, voluntary attendance, noninvasive measures, no deception, and appropriate physical and mental demands on the subject.

@@

We set out to recruit a sample of \(N\ge287\) teachers as determined using the R package \emph{pwr} (Champely, 2020), assuming a small to medium correlation of \(r=.20\) between the measures of interest and targeting at a power of \(1-\beta=.80\) at \(\alpha=.01\).
Teachers were recruited via social media, personal contacts to teachers, and to Saxon schools with the request to pass on the information.
All teachers were eligible, no payment was issued.
Of the \(N=\) 278 participants, who started filling out the online survey, \(N =\) 180 (72.20\% female, aged 20 to 67 years) data sets were complete and those participants indicated to have answered truthfully.
All of them were currently teaching at a primary, secondary, comprehensive, or vocational school.
Data was collected between the 12th of June and the 24th of July 2020.
At this point, schools had been switching between digital and hybrid forms of teaching for at least three months due to the Covid-19 pandemic, causing additional stress for many teachers.
This may have also be one reason why we did not reach our estimated sample size.
Using the smallest standardized indirect effect from the mediation in Grass et al. (2018) in a post hoc power analysis with \emph{G*Power} (Faul et al., 2007, 2009) yielded a power of \(1-\beta=.85\) for linear multiple regression, given \(\alpha=.05\), \(N=180\), and \(f^2=.05\).

@@

We used \emph{R Studio} (R Core Team, 2020; RStudio Team, 2020) with the main packages \emph{lavaan} (Rosseel, 2012) and \emph{psych} (Revelle, 2021) for all our analyses.
Data were checked for multivariate normality using Mardia's coefficient.
To account for non-linear relationships, correlations were computed using Spearman's rank coefficient rather than Pearson's product moment correlation.
Internal consistencies were assessed with Cronbach's Alpha and MacDonald's Omega.
Since Cronbach's Alpha has been criticized for being insensitive to violations of internal consistency (Dunn et al., 2014; Taber, 2018), the additional computation of MacDonald's Omega has the purpose of ensuring a more reliable estimation.
Correlations between variables were classified according the scheme by Gignac and Szodorai (2016), which recommends .10, .20, and .30 to be considered small, typical, and relatively large, respectively.

\hypertarget{replication-of-grass-et-al.-2018}{%
\subsubsection{Replication of Grass et al.~(2018)}\label{replication-of-grass-et-al.-2018}}
